NumLin: Linear Types for Linear Algebra

### 2019-04-12 write-up/paper/implementation.tex
Tidy up punctuation and figures
Fix formatting

\subsubsection{Desugaring, Matrix Expressions and Type Checking}\label{subsubsec:initial}

@@

\subsubsection{Type checking} is mostly standard for a linearly typed language,
with the exception of fractional permission inference. By restricting fractions
to be non-positive integer powers of two, we only need to keep track of the
logarithm of the fractions used. Explicit sharing and unsharing removes the
need for performing dataflow analysis. As a result, all fractional arithmetic
can be solved with unification, and in doing so, fractions become directly
usable in \lang's type-system as opposed to a convenient theoretical tool.

>>>>

\subsubsection{Desugaring, Matrix Expressions and Type Checking}

@@

\subsubsection{Type checking}

Type checking is mostly standard for a linearly typed language,
with the exception of fractional permission inference. By restricting fractions
to be non-positive integer powers of two, we only need to keep track of the
logarithm of the fractions used. Explicit sharing and unsharing removes the
need for performing dataflow analysis. As a result, all fractional arithmetic
can be solved with unification, and in doing so, fractions become directly
usable in \lang's type-system as opposed to a convenient theoretical tool.

### 2019-04-12 write-up/paper/lang_and_examples.tex
Fix formatting

\subsubsection{Factorial}

@@

The only argument is \highl{!x : !int}. The ! annotation on \texttt{x} is a
syntactic convenience for declaring the value to used intuitionistically, its
full and precise meaning is described in Section~\ref{subsubsec:initial}.

>>>>

\subsubsection{Factorial}\label{subsubsec:factorial}

@@

The only argument is \highl{!x : !int}. The ! annotation on \texttt{x} is a
syntactic convenience for declaring the value to used intuitionistically, its
full and precise meaning is described in Section~\ref{subsec:core_tt}.
